### 2019-12-06 reports/media/loosely_acc.tex
rename registers

  \node (hwacc1) at (3,0.2) [hwacc] {ACC};
  \begin{scope}[name=completeacc, local bounding box=accbb, shift={(3, 0.2)}]
    \node (reg0) [accint, minimum width=25pt, xshift=-5pt, minimum height=5pt, font=\tiny] {REG 0};
    \node (reg1) [accint, minimum width=25pt, minimum height=5pt, below=of reg0, font=\tiny] {REG 1};
    \node (reg2) [accint, minimum width=25pt, minimum height=5pt, below=of reg1, font=\tiny] {REG N};
    \node (spm) [accint, minimum height=15pt, minimum width=5pt, align=center,
    right=of reg0.north east, font=\tiny, anchor=north west] {S\\P\\M};
    \node (accpe) [accint, minimum width=10pt, minimum height=10pt, above=of reg0.north west,
    anchor=south west, font=\tiny] {PE};
    \node (accctl) [accint, minimum width=10pt, minimum height=10pt, above=of spm.north east,
    anchor=south east, font=\tiny] {CTL};
  \end{scope}
  \node (mainbus) at (-1, -2) [bus, anchor=west, minimum height=140pt] {};

>>>>

  \node (hwacc1) at (3,0.2) [hwacc] {ACC};
  \begin{scope}[name=completeacc, local bounding box=accbb, shift={(3, 0.2)}]
    \node (reg0) [accint, minimum width=25pt, xshift=-5pt, minimum height=5pt, font=\tiny] {MMR 0};
    \node (reg1) [accint, minimum width=25pt, minimum height=5pt, below=of reg0, font=\tiny] {MMR 1};
    \node (reg2) [accint, minimum width=25pt, minimum height=5pt, below=of reg1, font=\tiny] {MMR N};
    \node (spm) [accint, minimum height=15pt, minimum width=5pt, align=center,
    right=of reg0.north east, font=\tiny, anchor=north west] {S\\P\\M};
    \node (accpe) [accint, minimum width=10pt, minimum height=10pt, above=of reg0.north west,
    anchor=south west, font=\tiny] {PE};
    \node (accctl) [accint, minimum width=10pt, minimum height=10pt, above=of spm.north east,
    anchor=south east, font=\tiny] {CTL};
  \end{scope}
  \node (mainbus) at (-1, -2) [bus, anchor=west, minimum height=140pt] {};
